Concurrent Programming with CXL

### 2020-07-04 book/paper.tex

\newcommand{\cxllink}[1]{%
[\href{https://www.cs.cornell.edu/home/rvr/cxl/sources/#1}{\underline{#1}}]%
}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../code/Up.py}
\end{code}
\caption{[Up.py] Python implementation of Figure~\ref{fig:inc}.}
\label{fig:incpy}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../code/UpMany.py}
\end{code}
\caption{[UpMany.py] Incrementing \texttt{N} times.}
\label{fig:incmany}
\end{figure}

>>>>

\newcommand{\cxllink}[1]{%
[\href{https://www.cs.cornell.edu/home/rvr/cxl/code/#1}{\underline{#1}}]%
}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../code/Up.py}
\end{code}
\caption{\cxllink{Up.py} Python implementation of Figure~\ref{fig:inc}.}
\label{fig:incpy}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../code/UpMany.py}
\end{code}
\caption{\cxllink{UpMany.py} Incrementing \texttt{N} times.}
\label{fig:incmany}
\end{figure}
